Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-07-08 writeup/conStruct.tex
updated Peter's affiliation

\textsuperscript{2}
Department of Molecular and Computational Biology, 
University of Southern California, Los Angeles, CA 90089

@@

This work was supported in part by 
the National Science Foundation under award number NSF \#1262645 (DBI) to PR and GC, 
the National Institute of General Medical Sciences of the National Institutes of Health under award numbers NIH RO1GM83098 and RO1GM107374 to GC,
and the National Science Foundation under award numbers NSF \# 1148897 and \# 1402725 to GB.

>>>>

\textsuperscript{2}
Institute of Ecology and Evolution,
Department of Mathematics,
University of Oregon, Eugene, OR 97403

@@

We thank Marjorie Weber, William Wetzel, Mariah Meek, Yaniv Brandvain, and Matthew Stephens for invaluable comments on the method and manuscript, as well as attendees at the 2017 SSE Meeting in Portland, OR, whose votes determined the name of the method.
This work was supported in part by 
the National Science Foundation under award number NSF \#1262645 (DBI) to PR and GC, 
the National Institute of General Medical Sciences of the National Institutes of Health under award numbers NIH RO1GM83098 and RO1GM107374 to GC,
and the National Science Foundation under award numbers NSF \# 1148897 and \# 1402725 to GB.
